### 2016-04-01 document/manuscript-plos.tex
put tables sideways
update to affiliation
Fixed duplicated name

\usepackage{longtable}
\usepackage{booktabs}
\usepackage{array}

@@

Yasset Perez-RiverolYasset Perez-Riverol\textsuperscript{1,*}
Laurent Gatto\textsuperscript{2},
Rui Wang\textsuperscript{1}, 
Timo Sachsenberg \textsuperscript{3},
Julian Uszkoreit\textsuperscript{4},
Felipe da Veiga Leprevost\textsuperscript{5},
Christian Fufezan\textsuperscript{6},
Tobias Ternent\textsuperscript{1},
Stephen J. Eglen\textsuperscript{7}, 
Daniel S. Katz\textsuperscript{8}, 
Tom Pollard\textsuperscript{9}, 
Alexander Konovalov\textsuperscript{10},
Juan Antonio Vizcaíno\textsuperscript{1,*}

@@

\bf{1} European Molecular Biology Laboratory, European Bioinformatics
Institute (EMBL-EBI), Wellcome Trust Genome Campus, Hinxton,
Cambridge, CB10 1SD, UK.
\\
\bf{2} Computational Proteomics Unit, Cambridge Systems Biology
Centre, University of Cambridge, Tennis Court Road, Cambridge, CB2
1GA, UK.
\\
\bf{3} Applied Bioinformatics and Department of Computer Science,
University of Tübingen, D-72074 Tübingen, Germany.
\\
\bf{4} Medizinisches Proteom-Center, Ruhr-Universität Bochum,
Universitätsstr. 150, D-44801 Bochum, Germany.
\\
\bf{5} Department of Pathology, University of Michigan, Ann Arbor,
Michigan 48109, USA.
\\
\bf{6} Institute of Plant Biology and Biotechnology, University of
Muenster, Schlossplatz 8, 48143 Muenster, Germany.
\\
\bf{7} Centre for Mathematical Sciences, University of Cambridge,
Wilberforce Road, Cambridge CB3 0WA, UK.
\\
\bf{8} National Center for Supercomputing Applications, University of
Illinois, 1205 W. Clark St., Urbana, Illinois 61801, USA.
\\
\bf{9} MIT Laboratory for Computational Physiology, Institute for
Medical Engineering and Science, Massachusetts Institute of
Technology, E25-545B, 45 Carleton St, Cambridge, MA 02142, USA.
\\
\bf{10} Centre for Interdisciplinary Research in Computational
Algebra, University of St Andrews, St Andrews, Fife, KY16 9SX, UK.
\bigskip

>>>>

\usepackage{longtable}
\usepackage{booktabs}
\usepackage{array}
\usepackage{rotating}

@@

Yasset Perez-Riverol\textsuperscript{1,*}
Laurent Gatto\textsuperscript{2},
Rui Wang\textsuperscript{1}, 
Timo Sachsenberg \textsuperscript{3},
Julian Uszkoreit\textsuperscript{4},
Felipe da Veiga Leprevost\textsuperscript{5},
Christian Fufezan\textsuperscript{6},
Tobias Ternent\textsuperscript{1},
Stephen J. Eglen\textsuperscript{7}, 
Daniel S. Katz\textsuperscript{8}, 
Tom Pollard\textsuperscript{9}, 
Alexander Konovalov\textsuperscript{10},
Juan Antonio Vizcaíno\textsuperscript{1,*}

@@

\bf{1} European Molecular Biology Laboratory, European Bioinformatics
Institute (EMBL-EBI), Wellcome Trust Genome Campus, Hinxton,
Cambridge, CB10 1SD, UK.
\\
\bf{2} Computational Proteomics Unit, Cambridge Systems Biology
Centre, University of Cambridge, Tennis Court Road, Cambridge, CB2
1GA, UK.
\\
\bf{3} Applied Bioinformatics and Department of Computer Science,
University of Tübingen, D-72074 Tübingen, Germany.
\\
\bf{4} Medizinisches Proteom-Center, Ruhr-Universität Bochum,
Universitätsstr. 150, D-44801 Bochum, Germany.
\\
\bf{5} Department of Pathology, University of Michigan, Ann Arbor,
Michigan 48109, USA.
\\
\bf{6} Institute of Plant Biology and Biotechnology, University of
Muenster, Schlossplatz 8, 48143 Muenster, Germany.
\\
\bf{7} Centre for Mathematical Sciences, University of Cambridge,
Wilberforce Road, Cambridge CB3 0WA, UK.
\\
\bf{8} National Center for Supercomputing Applications \&
Graduate School of Library and Information Science, University of
Illinois, 1205 W. Clark St., Urbana, Illinois 61801, USA.
\\
\bf{9} MIT Laboratory for Computational Physiology, Institute for
Medical Engineering and Science, Massachusetts Institute of
Technology, E25-545B, 45 Carleton St, Cambridge, MA 02142, USA.
\\
\bf{10} Centre for Interdisciplinary Research in Computational
Algebra, University of St Andrews, St Andrews, Fife, KY16 9SX, UK.
\bigskip
